---
title: "Clarivate InCites API for Web of Science"
author: "John Muschelli"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Clarivate InCites API for Web of Science}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(webofscience)
```

# Introduction
The Web of Science or Web of Knowledge has a lot of bibliometric information about citations and publications.  We will show some examples for the the APIs we have access to.  All main functions have the prefix `ws_`.  All information is located at https://developer.clarivate.com/apis for the API specifications and requests for API keys.  Here we will show the InCites API.

# Incites API

The information from the InCites API can be found at https://developer.clarivate.com/apis/incites.  As this data cannot be shared, these examples will show you how to call the API, but not any of the results other than simple information.

Here we show the information about the InCites API:

```{r}
library(webofscience)
ws_list_apis()$incites
```

The key information is about where you can 

If you have an InCites API key, you can set it either in the `~/.Renviron` with the `r ws_list_apis()$incites$sys_env` variable  or using the `ws_set_incites_key` function:

```{r, eval = FALSE}
ws_set_incites_key(api_key = "YOUR_INCITES_API_KEY")
```

You can test if you have the API key set using:
```{r}
ws_have_incites_key()
```
which will return a logical.


## Calling the InCites API

### Incites Last Updated 
Here we will see the last time the data was updated:

```{r}
if (ws_have_incites_key()) {
  result = ws_incites_last_updated(flatten = TRUE)
  print(result$content$api$rval[[1]])
}
```

One can use the `lubridate` package to parse these dates. 

### Checking Valid UT

A UT is a Unique identifier for Web of Science Core Collection article.  We will use `ws_incites_invalid_ut` to determine  which UTs are invalid (if any):

```{r}
ut = c("000352040700014","000353267900023",
       "000346982900018","000346342200004")
if (ws_have_incites_key()) {
  valid_result = ws_incites_invalid_ut(ut = ut,
                                       flatten = TRUE)
  docs = valid_result$content$api$rval[[1]]
  print(docs)
  if (length(docs) > 0) {
    stop("Invalid UTs!")
  }
}
```

Above none are invalid.  Let us inject an invalid ID and see the result:

```{r}
if (ws_have_incites_key()) {
  invalid_result = ws_incites_invalid_ut(
    ut = c(ut,
           "0003463422000AB"),
    flatten = TRUE)
  docs = invalid_result$content$api$rval[[1]]
  print(docs)
}
```

We see the output is a `data.frame`.  If we want the invalid UTs, we can extract that one column:
```{r}
if (ws_have_incites_key()) {
  print(class(docs))
  print(docs$ISI_LOC)
}
```

We can then use `setdiff(ut, docs$ISI_LOC)` if we want to keep only the valid UTs.


### Getting Metrics by UT

If we want document metrics by UT, we can use `ws_incites_by_ut`.  We cannot show the output of the result, but we will show the names of the columns:

```{r}
if (ws_have_incites_key()) {
  
  result = ws_incites_by_ut(ut = ut,
                            flatten = TRUE)
  docs = result$content$api$rval[[1]]
  print(names(docs))
}
```


We can return InCites baseline metrics with Emerging Sources Citation Index (ESCI) content.  We show that they are not the same as those without, which was returned above:

```{r}
if (ws_have_incites_key()) {
  result_with_esci = ws_incites_by_ut(ut = ut,
                                      esci = TRUE,
                                      flatten = TRUE)
  docs_with_esci = result_with_esci$content$api$rval[[1]]
  print(all.equal(docs, docs_with_esci))
}
```

### Getting Metrics by Year

Here we show the output from `DocumentLevelMetricsByInstitutionIdRecordCount` endpoint, which gets metrics count by year.  We cannot show the output, but it is a scalar numeric:

```{r}
if (ws_have_incites_key()) {
  rec = ws_incites_by_record_count(
    year = current_year(),
    flatten = TRUE)
  print(length(rec$content$api$rval))
}
```

### Getting Metrics by Institution

This calls the `DocumentLevelMetricsByInstitutionId` endpoint Find all document level metrics for a given institution

```{r}
if (ws_have_incites_key()) {
  result = ws_incites_by_inst_id(
    year = current_year(),
    flatten = TRUE)
  docs = result$content$api$rval[[1]]
  print(colnames(docs))
}
```

Again we can return InCites metrics with ESCI content.  We show again that they are not the same as those without, which was returned above:

```{r}
if (ws_have_incites_key()) {
  result_with_esci = ws_incites_by_inst_id(
    year = current_year(),
    flatten = TRUE, esci = "y")
  esci_docs = result_with_esci$content$api$rval[[1]]
  print(all.equal(docs, esci_docs))
}
```
